Event History Analysis for psychological time-to-event data: A tutorial in R with examples in Bayesian and frequentist workflows

### 2024-12-09 manuscript/manuscript.Rmd
update ms

```{r table-grand-ame}
 apa_table(
   tab_grand_ame,
   caption = "(ref:table-grand-ame-caption)",
   note = "(ref:table-grand-ame-note-caption)",
   placement = "H",
#   font_size = "scriptsize",
   longtable = TRUE,
   repeat_header = TRUE,
   format.args = list(
        digits = c(0,0,2,2,2),
        decimal.mark = ".", big.mark = "")
)
```

>>>>

```{r table-grand-ame, eval = F}
 apa_table(
   tab_grand_ame,
   caption = "(ref:table-grand-ame-caption)",
   note = "(ref:table-grand-ame-note-caption)",
   placement = "H",
#   font_size = "scriptsize",
   longtable = TRUE,
   repeat_header = TRUE,
   format.args = list(
        digits = c(0,0,2,2,2),
        decimal.mark = ".", big.mark = "")
)
```
